---
title: "pstat 131 homework 2"
author: "Shefali Singh"
date: '2022-04-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
library(ggplot2)
library(corrplot)
library(ggthemes)
tidymodels_prefer()
library(yardstick)
```
Homework 2

1. 
```{r}
abalone <- read.csv("Desktop/abalone.csv")
abalone$age <- abalone$rings + 1.5
hist(abalone$age)
shapiro.test(abalone$age)
```
As can be seen from the histogram, the distribution of age is right skewed, and the Shapiro-Wilk test for normality has a p value of < 2.2e-16, meaning the null (the data are normally distributed) can be rejected.

2. 
```{r}
set.seed(3435)
abalone_split <- initial_split(abalone, prop=0.80, strata=age)
abalone_train <- training(abalone_split)
abalone_test <- testing(abalone_split)
```

3. 
```{r}
abalone_recipe <- recipe(age ~ type + longest_shell + diameter + height + whole_weight + shucked_weight + viscera_weight + shell_weight, data = abalone_train) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_interact(terms = ~ type:shucked_weight + longest_shell:diameter + shucked_weight:shell_weight) %>%
  step_normalize(all_numeric())
```
Rings should not be used to predict age as it is simply the amount of rings + 1.5 and thus directly predicts age alone without input from other predictors.

4. 
```{r}
lm_model <- linear_reg()%>%
  set_engine("lm")
```

5. 
```{r}
lm_wflow <- workflow() %>%
  add_model(lm_model) %>%
  add_recipe(abalone_recipe)
lm_fit <- fit(lm_wflow, abalone_train)
```

6. 
```{r}
lm_fit
5.36988 - 0.02088*0.5 + 10.74518*0.1 + 9.23360*0.3 + 7.65812*4 - 18.27074 - 9.39532*2 + 10.63978
```
The predicted age is 13.41492.

7. 
```{r}
summary(lm_fit)

```

